A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-14 Paper.tex
Added UWB and WIFI section
added a UWB and WIFI paragraph, also rephrased to WSN section to focus more on the fact that several surveys exist for specific things (zigbee, 802,etc)

			  	\begin{figure}[h!]
					\centering
				%	\includegraphics[width=90mm]{DNR.png}
				%	\includegraphics[width=90mm]{DNR.png}	
					\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
					\label{DNR}
				\end{figure}

@@

			Wireless sensors networks (WSN) are also a very popular choice, especially since many of them come with the ability to transmit RSSI. \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.  \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more. \cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards. \cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations. \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.

@@

			%M. Oca ̃na, L. M. Bergasa, M. A. Sotelo, R. F. Flores, D. F.  ́
			%Llorca, and D. Schleicher, “Automatic training method applied to
			a% WiFi+ultrasound POMDP navigation system,” Robotica, vol. 27,
			%no. 07, pp. 1049–1061, December 2009.

>>>>

	%		  	\begin{figure}[h!]
	%				\centering
				%	\includegraphics[width=90mm]{DNR.png}
	%				\includegraphics[width=90mm]{DNR.png}	
	%				\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
	%				\label{DNR}
	%			\end{figure}

@@

			Ultra-wideband radios are another popular choice. One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms. \cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.

			Wireless Fidelity (wi-fi)  is another choice being explored by man researchers as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}. \cite{Youssef2005} presents a Horus system with the aim of high accuracy and low computation cost for wireless local area network location determining. \cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing. \cite{Kotaru2015} presents a design and implementation for its SpotFi system which can be deployed on top of existing wi-fi infrastructure. \cite{Rea2017} designed a new method for filtering range measurment specifically designed with the large noise found in indoor WiFi radios in mind.

			 \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to wireless sensor networks.  \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more. \cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards. \cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations. \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.

@@

			%M. Oca ̃na, L. M. Bergasa, M. A. Sotelo, R. F. Flores, D. F.  ́
			%Llorca, and D. Schleicher, “Automatic training method applied to
			% WiFi+ultrasound POMDP navigation system,” Robotica, vol. 27,
			%no. 07, pp. 1049–1061, December 2009.
